Robust Subspace and Higher Moments Distances for Botnet Detection

### 2019-04-24 docs/papers/2019JNCA_m-rpca/2019JNCA_m-rpca.tex
conclude robpca and initiate justificative for imbalance and skewness

Some techniques can make the data discriminative for better anomaly detection: Data engineering (i.e. sampling \cite{??}, aggregation \cite{callegari2011novel, acarali2016survey}); Feature extraction (i.e. decomposition \cite{??}, robust estimates \cite{??}).

@@

Network anomaly detection problems are usually characterized by skewed and imbalanced data \cite{Phua2004minority}.

Learning algorithms for imbalanced data has been a relevant research topic.

The fundamental issue with the imbalanced learning problem is the ability of imbalanced data to significantly compromise the performance of most standard learning algorithms \cite{he2008learning}.

@@

Principal Component Analysis (PCA) is a statistical technique commonly used for dimensionality reduction. It uses an orthogonal transformation to convert a set of correlated variables into a set of linearly uncorrelated variables, where the first principal components have the largest variance. PCA has been used in attack detection \cite{almotairi2009technique}. However, PCA requires human intervention in order to identify abnormalities based on the eigenvalues profiles, if used without complementary techniques. Callegari \emph{et al} \cite{callegari2011novel} propose a PCA-based method for identifying the traffic flows responsible for an anomaly detected at the aggregate level and evaluated their proposal through a dataset with synthetic anomalies added in the data. However, Callegari \emph{et al} focus on flood attack detection, not addressing probe attack detection, and their approach relies on visual analysis. CAllegari separate normal of anomalies according to principal components (normal) and remaining (anomalies), based on PCA. It relies in the assumption that anomalies will cause a large change into anomalous components. This is similar to our previous work, but we rely on change into principal eigenvectors.

@@

ROBPCA \cite{hubert2005robpca} intends to identify outliers using PCA to reduce the data dimensions and plot the orthogonal distances versus the score distances, to flag outliers using an outlier map. However, ROBPCA flags many points as outlying when the original data is skewed. To overcome that issue, \cite{hubert2009robustskewed} propose ROBPCA-AO, which relies on an adjusted outlyingness based on robust skewness for flagging outliers....

@@

\textbf{The C-step can be algorithmically described as follows:}
\begin{algorithm}[H]\label{alg:alg01}
	\scriptsize
	\SetAlgoLined
	\KwResult{$\boldsymbol{\bar{x}}_2$, $\boldsymbol{\hat{S}}_2$}
	Given the initial $h-$subset $\boldsymbol{h}_1$ of indexes or the pair $(\boldsymbol{\bar{x}}_1, \boldsymbol{\hat{S}}_1)$\;
	\While{$det(\boldsymbol{\hat{S}}_2) < det(\boldsymbol{\hat{S}}_1)$}{
		\If{$\boldsymbol{\bar{x}}_2$ and $\boldsymbol{\hat{S}}_2$ exist}{
			Put $\boldsymbol{\bar{x}}_1 = \boldsymbol{\bar{x}}_2$ and $\boldsymbol{\hat{S}}_1 = \boldsymbol{\hat{S}}_2$\;
		}
		Compute the distances $\boldsymbol{d}_1( i )$ for $i = 1,..., n$\;
		Sort $\boldsymbol{d}_1( i )$, which yields a index $\boldsymbol{d}_1(\pi(1)) \leq ... \leq \boldsymbol{d}_1(\pi(n))$\;
		Put $\boldsymbol{h}_2 = \{ \pi(1), \pi(2), ..., \pi(h)\}$\;
		Compute $\boldsymbol{\bar{x}}_2$ and $\boldsymbol{\hat{S}}_2$ for $\boldsymbol{h}_2$\;
		Compute $det(\boldsymbol{\hat{S}}_2)$ and $det(\boldsymbol{\hat{S}}_1)$\;			
	}
	\caption{C-Step}
\end{algorithm}

@@

\textbf{Initial subset can be algorithmically described as:}
\begin{algorithm}[H]\label{alg:alg02}
	\scriptsize
	\SetAlgoLined
	\KwResult{$\boldsymbol{h}_1$}
	Given a data set $\boldsymbol{X} \in \mathbb{R}^{n \times p}$ with $p$-variate observations\;
	Draw a random $(p + 1)$-subset $\boldsymbol{L}$\;
	Compute $\boldsymbol{\bar{x}}_1$ and $\boldsymbol{\hat{S}}_1$ of $\boldsymbol{L}$ and $det(\boldsymbol{\hat{S}}_1)$\;
	\If{$det(\boldsymbol{\hat{S}}_1) \leq 0$}{
		Add another random observation into $\boldsymbol{L}$\;
		Compute $\boldsymbol{\bar{x}}_1$ and $\boldsymbol{\hat{S}}_1$ of $\boldsymbol{L}$ and $det(\boldsymbol{\hat{S}}_1)$\;
	}
	Compute $\boldsymbol{d}_1^2(i) = (\boldsymbol{x}_i - \boldsymbol{\bar{x}}_1)^\prime \boldsymbol{\hat{S}}_1^{-1}(\boldsymbol{X}_i - \boldsymbol{\bar{x}}_0)$ for $i = 1, ..., n$\;
	Sort them into $\boldsymbol{d}_1(\pi(1)) \leq ... \leq \boldsymbol{d}_0(\pi(n))$\;
	Put $\boldsymbol{h}_1 = \{\pi(1), ..., \pi(h)\}$\;
	\caption{Constructing the initial subset}
\end{algorithm}

\begin{algorithm}[H]\label{alg:alg03}
	\scriptsize
	\SetAlgoLined
	\KwResult{$\boldsymbol{\bar{x}}_2$, $\boldsymbol{\hat{S}}_2$}
	Given $\boldsymbol{X} \in \mathbb{R}^{n \times p}$, $h < n$, $p \geq 2$ and $n \leq 600$\;
	\For{500 times}{
		Construct initial $h$-subset $\boldsymbol{h}_1$ (Algorithm \ref{alg:alg02})\;
		Carry out two C-steps (Algorithm \ref{alg:alg01}) resulting $\boldsymbol{\bar{x}}_2$ and $\boldsymbol{\hat{S}}_2$\;
	}		
	Put $\boldsymbol{h}_1$ as the 10 lowest $det(\boldsymbol{\hat{S}_2})$ computed above\;
	\While{$det(\boldsymbol{\hat{S}}_2) < det(\boldsymbol{\hat{S}}_1)$}{
		Carry out C-steps (Algorithm \ref{alg:alg01})\;
	}
	\caption{Fast-MCD when $n \leq 600$}
\end{algorithm}

\begin{algorithm}[H]\label{alg:alg04}
	\scriptsize
	\SetAlgoLined
	\KwResult{$\boldsymbol{\bar{x}}_2$, $\boldsymbol{\hat{S}}_2$}
	Given $\boldsymbol{X} \in \mathbb{R}^{n \times p}$, $h < n$, $p \geq 2$ and $n > 600$\;
	Construct up to 5 disjoint random subsets of size $n_{sub} = 300$\;
	\For{each subset, repeat 100 times}{
		Construct initial $\boldsymbol{h}_1$ of size $h_{sub} = [n_{sub}(h/n)]$\;
		Carry out two C-steps of $n_{sub}$ and $h_{sub}$\;
		Keep the 10 best $(\boldsymbol{\bar{x}}_{sub}, \boldsymbol{\hat{S}}_{sub})$\;
	}		
	Pool the subsets, yielding the merged set of $n_{merged} = 1500$\;
	\For{50 best $(\boldsymbol{\bar{x}}_{sub}, \boldsymbol{\hat{S}}_{sub})$}{
		Carry out two C-steps of $n_{merged}$ and $h_{merged} = [n_{merged}(h/n)]$\;
		Keep the 10 best $(\boldsymbol{\bar{x}}_{merged}, \boldsymbol{\hat{S}}_{merged})$\;
	}
	\For{the full data set and $m_{full}$ best results}{
		Take several C-steps, using $n$ and $h$\;
		Keep the best final result $(\boldsymbol{\bar{x}}_{full}, \boldsymbol{\hat{S}}_{full})$\;
	}
	\caption{Fast-MCD when $n > 600$}
\end{algorithm}

@@

He and Garcia \cite{he2008learning} present a classification of imbalanced learning methods as sampling, cost-sensitive learning, kernel-based, and active learning.

Data aggregation is a widely adoted approach for feature engineering \cite{chandrashekar2014survey,acarali2016survey}.

@@

\begin{algorithm}[H]\label{alg:alg05}
	\scriptsize
	\SetAlgoLined
	\KwResult{$\boldsymbol{\bar{x}}_2$, $\boldsymbol{\hat{S}}_2$, $\boldsymbol{\bar{s}}_2$ and $\boldsymbol{\bar{k}}_2$}
	Given the initial $h-$subset $\boldsymbol{h}_1$ of indexes or the pair $(\boldsymbol{\bar{x}}_1, \boldsymbol{\hat{S}}_1)$\;
	\While{$det(\boldsymbol{\hat{S}}_2) < det(\boldsymbol{\hat{S}}_1)$}{
		\If{$\boldsymbol{\bar{x}}_2$ and $\boldsymbol{\hat{S}}_2$ exist}{
			Put $\boldsymbol{\bar{x}}_1 = \boldsymbol{\bar{x}}_2$ and $\boldsymbol{\hat{S}}_1 = \boldsymbol{\hat{S}}_2$\;
		}
		Compute the distances $\boldsymbol{d}_1( i )$ for $i = 1,..., n$\;
		Sort $\boldsymbol{d}_1( i )$, which yields a index $\boldsymbol{d}_1(\pi(1)) \leq ... \leq \boldsymbol{d}_1(\pi(n))$\;
		Put $\boldsymbol{h}_2 = \{ \pi(1), \pi(2), ..., \pi(h)\}$\;
		Compute $\boldsymbol{\bar{x}}_2$ and $\boldsymbol{\hat{S}}_2$ for $\boldsymbol{h}_2$\;
		Compute $det(\boldsymbol{\hat{S}}_2)$ and $det(\boldsymbol{\hat{S}}_1)$\;			
	}
	Compute $\boldsymbol{\bar{s}}_2$ and $\boldsymbol{\bar{k}}_2$ for last $\boldsymbol{h}_2$\;
	\caption{C-Step with higher moments}
\end{algorithm}

@@

\begin{algorithm}[H]\label{alg:alg06}
	\scriptsize
	\SetAlgoLined
	\KwResult{$\boldsymbol{\bar{x}}_2$, $\boldsymbol{\hat{S}}_2$, $\boldsymbol{\bar{s}}_2$ and $\boldsymbol{\bar{k}}_2$}
	Given $\boldsymbol{X} \in \mathbb{R}^{n \times p}$, $h < n$, $p \geq 2$ and $n \leq 600$\;
	\For{500 times}{
		Construct initial $h$-subset $\boldsymbol{h}_1$ (Algorithm \ref{alg:alg02})\;
		Carry out two C-steps with higher moments (Algorithm \ref{alg:alg05}) resulting $\boldsymbol{\bar{x}}_2$, $\boldsymbol{\hat{S}}_2$, $\boldsymbol{\bar{s}}_2$ and $\boldsymbol{\bar{k}}_2$\;
	}		
	Put $\boldsymbol{h}_1$ as the 10 lowest $det(\boldsymbol{\hat{S}_2})$ computed above\;
	\While{$det(\boldsymbol{\hat{S}}_2) < det(\boldsymbol{\hat{S}}_1)$}{
		Carry out C-steps with higher moments (Algorithm \ref{alg:alg05})\;
	}
	\caption{Fast-MCD with higher moments when $n \leq 600$}
\end{algorithm}

@@

\begin{algorithm}[H]\label{alg:alg07}
	\scriptsize
	\SetAlgoLined
	\KwResult{$\boldsymbol{\bar{x}}_2$, $\boldsymbol{\hat{S}}_2$, $\boldsymbol{\bar{s}}_2$ and $\boldsymbol{\bar{k}}_2$}
	Given $\boldsymbol{X} \in \mathbb{R}^{n \times p}$, $h < n$, $p \geq 2$ and $n > 600$\;
	Construct up to 5 disjoint random subsets of size $n_{sub} = 300$\;
	\For{each subset, repeat 100 times}{
		Construct initial $\boldsymbol{h}_1$ of size $h_{sub} = [n_{sub}(h/n)]$\;
		Carry out two C-steps with higher moments of $n_{sub}$ and $h_{sub}$\;
		Keep the 10 best $(\boldsymbol{\bar{x}}_{sub}, \boldsymbol{\hat{S}}_{sub}, \boldsymbol{\bar{s}}_{sub}, \boldsymbol{\bar{k}}_{sub})$\;
	}		
	Pool the subsets, yielding the merged set of $n_{merged} = 1500$\;
	\For{50 best $(\boldsymbol{\bar{x}}_{sub}, \boldsymbol{\hat{S}}_{sub})$}{
		Carry out two C-steps with higher moments of $n_{merged}$ and $h_{merged} = [n_{merged}(h/n)]$\;
		Keep the 10 best $(\boldsymbol{\bar{x}}_{merged}, \boldsymbol{\hat{S}}_{merged}, \boldsymbol{\bar{s}}_{merged}, \boldsymbol{\bar{k}}_{merged})$\;
	}
	\For{the full data set and $m_{full}$ best results}{
		Take several C-steps, using $n$ and $h$\;
		Keep the best final result $(\boldsymbol{\bar{x}}_{full}, \boldsymbol{\hat{S}}_{full}, \boldsymbol{\bar{s}}_{full}, \boldsymbol{\bar{k}}_{full})$\;
	}
	\caption{Fast-MCD with higher moments when $n > 600$}
\end{algorithm}

@@

		In anomalous detection problems, where anomalies are rare events, if we classify all observations as normal and apply a accuracy evaluation, we would have high accuracy but poor true-positive detection.
		Due to the importance given by F-measure to true-positive detection \cite{moustafa2019holistic}, the F-measure is the preferable measure for imbalanced data sets.

>>>>

@@

Network anomaly detection problems are usually characterized by skewed and imbalanced data \cite{Phua2004minority,he2008learning}. Learning algorithms for imbalanced data has been a challenging research topic. The fundamental issue with the imbalanced learning problem is the ability of imbalanced data to significantly compromise the performance of most standard learning algorithms \cite{he2008learning}. He and Garcia \cite{he2008learning} present a classification of imbalanced learning methods as sampling, cost-sensitive learning, kernel-based, and active learning. Some techniques can make the data discriminative for better discriminative analytics: Data engineering (i.e. sampling \cite{he2008learning}, aggregation \cite{callegari2011novel, acarali2016survey}); Feature extraction (i.e. decomposition \cite{vaswani2018robust}, robust estimates \cite{zhou2017anomaly}). To face a high imbalanced data set, we adopt a sampling method based on data aggregation for discriminative feature generation, considering that data aggregation is a widely adoted approach for feature engineering \cite{chandrashekar2014survey,acarali2016survey} and network anomaly detection \cite{lakhina2005mining, callegari2011novel, vieira2017model}.

Some approaches assume a gaussian distribute data, hoever it is not true in real world for many fields....Data skewness...

@@

Principal Component Analysis (PCA) is a statistical technique commonly used for dimensionality reduction. It uses an orthogonal transformation to convert a set of correlated variables into a set of linearly uncorrelated variables, where the first principal components have the largest variance. PCA has been used in attack detection \cite{almotairi2009technique}. However, PCA requires human intervention in order to identify abnormalities based on the eigenvalues profiles, if used without complementary techniques. Callegari \emph{et al} \cite{callegari2011novel} propose a PCA-based method for identifying the traffic flows responsible for an anomaly detected at the aggregate level and evaluated their proposal through a dataset with synthetic anomalies added in the data. However, Callegari \emph{et al} focus on flood attack detection, not addressing probe attack detection, and their approach relies on visual analysis. Callegari separate normal of anomalies according to principal components (normal) and remaining (anomalies), based on PCA. It relies in the assumption that anomalies will cause a large change into anomalous components. This is similar to our previous work, but we rely on change into principal eigenvectors.

@@

ROBPCA \cite{hubert2005robpca} intends to identify outliers using PCA from robust estimates of location and scatter matrix, to reduce the data dimensions and plotting the orthogonal distances versus the robust score distances, to flag an outlier map. However, ROBPCA flags many points as outlying when the original data is skewed. To overcome that issue, \cite{hubert2009robustskewed} propose ROBPCA-AO, which improve ROBPCA by means of an adjusted outlyingness based on robust skewness. In contrast to our proposal, ROBPCA and ROBPCA-AO rely on a previously defined cutoff value for classify anomalous observations, and does not require training.

@@

\textbf{The C-step can be algorithmically described as follows:}
\begin{algorithm}
	\label{alg:alg01}
	\scriptsize
	\SetAlgoLined
	\KwResult{$\boldsymbol{\bar{x}}_2$, $\boldsymbol{\hat{S}}_2$}
	Given the initial $h-$subset $\boldsymbol{h}_1$ of indexes or the pair $(\boldsymbol{\bar{x}}_1, \boldsymbol{\hat{S}}_1)$\;
	\While{$det(\boldsymbol{\hat{S}}_2) < det(\boldsymbol{\hat{S}}_1)$}{
		\If{$\boldsymbol{\bar{x}}_2$ and $\boldsymbol{\hat{S}}_2$ exist}{
			Put $\boldsymbol{\bar{x}}_1 = \boldsymbol{\bar{x}}_2$ and $\boldsymbol{\hat{S}}_1 = \boldsymbol{\hat{S}}_2$\;
		}
		Compute the distances $\boldsymbol{d}_1( i )$ for $i = 1,..., n$\;
		Sort $\boldsymbol{d}_1( i )$, which yields an index $\boldsymbol{d}_1(\pi(1)) \leq ... \leq \boldsymbol{d}_1(\pi(n))$\;
		Put $\boldsymbol{h}_2 = \{ \pi(1), \pi(2), ..., \pi(h)\}$\;
		Compute $\boldsymbol{\bar{x}}_2$ and $\boldsymbol{\hat{S}}_2$ for $\boldsymbol{h}_2$\;
		Compute $det(\boldsymbol{\hat{S}}_2)$ and $det(\boldsymbol{\hat{S}}_1)$\;			
	}
	\caption{C-Step}
\end{algorithm}

@@

\textbf{Initial subset can be algorithmically described as:}
\begin{algorithm}
	\label{alg:alg02}
	\scriptsize
	\SetAlgoLined
	\KwResult{$\boldsymbol{h}_1$}
	Given a data set $\boldsymbol{X} \in \mathbb{R}^{n \times p}$ with $p$-variate observations\;
	Draw a random $(p + 1)$-subset $\boldsymbol{L}$\;
	Compute $\boldsymbol{\bar{x}}_1$ and $\boldsymbol{\hat{S}}_1$ of $\boldsymbol{L}$ and $det(\boldsymbol{\hat{S}}_1)$\;
	\If{$det(\boldsymbol{\hat{S}}_1) \leq 0$}{
		Add another random observation into $\boldsymbol{L}$\;
		Compute $\boldsymbol{\bar{x}}_1$ and $\boldsymbol{\hat{S}}_1$ of $\boldsymbol{L}$ and $det(\boldsymbol{\hat{S}}_1)$\;
	}
	Compute $\boldsymbol{d}_1^2(i) = (\boldsymbol{x}_i - \boldsymbol{\bar{x}}_1)^\prime \boldsymbol{\hat{S}}_1^{-1}(\boldsymbol{X}_i - \boldsymbol{\bar{x}}_0)$ for $i = 1, ..., n$\;
	Sort them into $\boldsymbol{d}_1(\pi(1)) \leq ... \leq \boldsymbol{d}_0(\pi(n))$\;
	Put $\boldsymbol{h}_1 = \{\pi(1), ..., \pi(h)\}$\;
	\caption{Constructing the initial subset}
\end{algorithm}

\begin{algorithm}
	\label{alg:alg03}
	\scriptsize
	\SetAlgoLined
	\KwResult{$\boldsymbol{\bar{x}}_2$, $\boldsymbol{\hat{S}}_2$}
	Given $\boldsymbol{X} \in \mathbb{R}^{n \times p}$, $h < n$, $p \geq 2$ and $n \leq 600$\;
	\For{500 times}{
		Construct initial $h$-subset $\boldsymbol{h}_1$ (Algorithm \ref{alg:alg02})\;
		Carry out two C-steps (Algorithm \ref{alg:alg01}) resulting $\boldsymbol{\bar{x}}_2$ and $\boldsymbol{\hat{S}}_2$\;
	}		
	Put $\boldsymbol{h}_1$ as the 10 lowest $det(\boldsymbol{\hat{S}_2})$ computed above\;
	\While{$det(\boldsymbol{\hat{S}}_2) < det(\boldsymbol{\hat{S}}_1)$}{
		Carry out C-steps (Algorithm \ref{alg:alg01})\;
	}
	\caption{Fast-MCD when $n \leq 600$}
\end{algorithm}

\begin{algorithm}
	\label{alg:alg04}
	\scriptsize
	\SetAlgoLined
	\KwResult{$\boldsymbol{\bar{x}}_2$, $\boldsymbol{\hat{S}}_2$}
	Given $\boldsymbol{X} \in \mathbb{R}^{n \times p}$, $h < n$, $p \geq 2$ and $n > 600$\;
	Construct up to 5 disjoint random subsets of size $n_{sub} = 300$\;
	\For{each subset, repeat 100 times}{
		Construct initial $\boldsymbol{h}_1$ of size $h_{sub} = [n_{sub}(h/n)]$\;
		Carry out two C-steps of $n_{sub}$ and $h_{sub}$\;
		Keep the 10 best $(\boldsymbol{\bar{x}}_{sub}, \boldsymbol{\hat{S}}_{sub})$\;
	}		
	Pool the subsets, yielding the merged set of $n_{merged} = 1500$\;
	\For{50 best $(\boldsymbol{\bar{x}}_{sub}, \boldsymbol{\hat{S}}_{sub})$}{
		Carry out two C-steps of $n_{merged}$ and $h_{merged} = [n_{merged}(h/n)]$\;
		Keep the 10 best $(\boldsymbol{\bar{x}}_{merged}, \boldsymbol{\hat{S}}_{merged})$\;
	}
	\For{the full data set and $m_{full}$ best results}{
		Take several C-steps, using $n$ and $h$\;
		Keep the best final result $(\boldsymbol{\bar{x}}_{full}, \boldsymbol{\hat{S}}_{full})$\;
	}
	\caption{Fast-MCD when $n > 600$}
\end{algorithm}

@@

@@

\begin{algorithm}
	\label{alg:alg05}
	\scriptsize
	\SetAlgoLined
	\KwResult{$\boldsymbol{\bar{x}}_2$, $\boldsymbol{\hat{S}}_2$, $\boldsymbol{\bar{s}}_2$ and $\boldsymbol{\bar{k}}_2$}
	Given the initial $h-$subset $\boldsymbol{h}_1$ of indexes or the pair $(\boldsymbol{\bar{x}}_1, \boldsymbol{\hat{S}}_1)$\;
	\While{$det(\boldsymbol{\hat{S}}_2) < det(\boldsymbol{\hat{S}}_1)$}{
		\If{$\boldsymbol{\bar{x}}_2$ and $\boldsymbol{\hat{S}}_2$ exist}{
			Put $\boldsymbol{\bar{x}}_1 = \boldsymbol{\bar{x}}_2$ and $\boldsymbol{\hat{S}}_1 = \boldsymbol{\hat{S}}_2$\;
		}
		Compute the distances $\boldsymbol{d}_1( i )$ for $i = 1,..., n$\;
		Sort $\boldsymbol{d}_1( i )$, which yields an index $\boldsymbol{d}_1(\pi(1)) \leq ... \leq \boldsymbol{d}_1(\pi(n))$\;
		Put $\boldsymbol{h}_2 = \{ \pi(1), \pi(2), ..., \pi(h)\}$\;
		Compute $\boldsymbol{\bar{x}}_2$ and $\boldsymbol{\hat{S}}_2$ for $\boldsymbol{h}_2$\;
		Compute $det(\boldsymbol{\hat{S}}_2)$ and $det(\boldsymbol{\hat{S}}_1)$\;			
	}
	Compute $\boldsymbol{\bar{s}}_2$ and $\boldsymbol{\bar{k}}_2$ for last $\boldsymbol{h}_2$\;
	\caption{C-Step with higher moments}
\end{algorithm}

@@

\begin{algorithm}
	\label{alg:alg06}
	\scriptsize
	\SetAlgoLined
	\KwResult{$\boldsymbol{\bar{x}}_2$, $\boldsymbol{\hat{S}}_2$, $\boldsymbol{\bar{s}}_2$ and $\boldsymbol{\bar{k}}_2$}
	Given $\boldsymbol{X} \in \mathbb{R}^{n \times p}$, $h < n$, $p \geq 2$ and $n \leq 600$\;
	\For{500 times}{
		Construct initial $h$-subset $\boldsymbol{h}_1$ (Algorithm \ref{alg:alg02})\;
		Carry out two C-steps with higher moments (Algorithm \ref{alg:alg05}) resulting $\boldsymbol{\bar{x}}_2$, $\boldsymbol{\hat{S}}_2$, $\boldsymbol{\bar{s}}_2$ and $\boldsymbol{\bar{k}}_2$\;
	}		
	Put $\boldsymbol{h}_1$ as the 10 lowest $det(\boldsymbol{\hat{S}_2})$ computed above\;
	\While{$det(\boldsymbol{\hat{S}}_2) < det(\boldsymbol{\hat{S}}_1)$}{
		Carry out C-steps with higher moments (Algorithm \ref{alg:alg05})\;
	}
	\caption{Fast-MCD with higher moments when $n \leq 600$}
\end{algorithm}

@@

\begin{algorithm}
	\label{alg:alg07}
	\scriptsize
	\SetAlgoLined
	\KwResult{$\boldsymbol{\bar{x}}_2$, $\boldsymbol{\hat{S}}_2$, $\boldsymbol{\bar{s}}_2$ and $\boldsymbol{\bar{k}}_2$}
	Given $\boldsymbol{X} \in \mathbb{R}^{n \times p}$, $h < n$, $p \geq 2$ and $n > 600$\;
	Construct up to 5 disjoint random subsets of size $n_{sub} = 300$\;
	\For{each subset, repeat 100 times}{
		Construct initial $\boldsymbol{h}_1$ of size $h_{sub} = [n_{sub}(h/n)]$\;
		Carry out two C-steps with higher moments of $n_{sub}$ and $h_{sub}$\;
		Keep the 10 best $(\boldsymbol{\bar{x}}_{sub}, \boldsymbol{\hat{S}}_{sub}, \boldsymbol{\bar{s}}_{sub}, \boldsymbol{\bar{k}}_{sub})$\;
	}		
	Pool the subsets, yielding the merged set of $n_{merged} = 1500$\;
	\For{50 best $(\boldsymbol{\bar{x}}_{sub}, \boldsymbol{\hat{S}}_{sub})$}{
		Carry out two C-steps with higher moments of $n_{merged}$ and $h_{merged} = [n_{merged}(h/n)]$\;
		Keep the 10 best $(\boldsymbol{\bar{x}}_{merged}, \boldsymbol{\hat{S}}_{merged}, \boldsymbol{\bar{s}}_{merged}, \boldsymbol{\bar{k}}_{merged})$\;
	}
	\For{the full data set and $m_{full}$ best results}{
		Take several C-steps, using $n$ and $h$\;
		Keep the best final result $(\boldsymbol{\bar{x}}_{full}, \boldsymbol{\hat{S}}_{full}, \boldsymbol{\bar{s}}_{full}, \boldsymbol{\bar{k}}_{full})$\;
	}
	\caption{Fast-MCD with higher moments when $n > 600$}
\end{algorithm}

@@

		In anomalous detection problems, where anomalies are rare events, if we classify all observations as normal and apply an accuracy evaluation, we would have high accuracy but poor true-positive detection.
		Due to the importance given by F-measure to true-positive detection \cite{moustafa2019holistic}, the F-measure is the preferable measure for imbalanced data sets.
